### 2016-06-27 notes/Marillia/Jun23-2016/notes.tex
ran leto's analysis on Barger and Butler

\begin{centering}
  \large {\bf The assembly of plant-pollinator communities in response
  to restoration8} \\
\end{centering}
\vspace{0.15in}

\section{Questions}
\begin{enumerate}
\item Determine whether there are change points in the assmebly of the
  ``maturing'' hedgerow communties, and compare those to the
  ``mature'' and ``unrestored''
\item Examine the resileicen of the maturing communities through time,
  as well as the different site types
\item Simulate the extinction of plants affected by drought, and see
  if the predict extinct pollinator species that are 
\item Assess whether (and how) species roles/importance are changing
  through time, as community matures. 
\end{enumerate}

>>>>

\begin{centering}
  \large {\bf The assembly of plant-pollinator communities in response
    to restoration} \\
\end{centering}
\vspace{0.15in}

\section{Questions}
\begin{enumerate}
\item Do the maturing hedgerows undergo a change point during
  assembly? Is that change point associated with drought? Do the
  ``controls'', unrestored and mature hedgerows undergo a change point
  in responce to drought similar to the maturing hedgerows?
\item Even if the network isn't shifting drastically, are the roles of
  species changing? Assess whether (and how) species roles/importance
  are changing through time, as community matures.
\item Are the maturing hedgerows getting more resilient through
  time? Examine the resilience of the maturing communities through time,
  as well as the different site types
\item can we predict the fate of pollinator species to ``exctinction''
  of their plants in response to drought? Simulate the extinction of
  plants affected by drought, and see if the predict extinct
  pollinator species that are
\end{enumerate}
